---
title: RMarkdown Viz Test
author: David E. Lambert
output:
  html_document:
    toc: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup & Import
```{r import, message=FALSE}

# deatch all non-base packages
# lapply(paste('package:',names(sessionInfo()$otherPkgs),sep=""),
#        detach, character.only=TRUE, unload=TRUE)

# clear environment
rm(list = ls())


# some libraries we'll use
library(GGally)
library(plotly)
library(RColorBrewer)
library(tidyverse)

# 330 county panel data for 2008, 2012, 2016 presidential elections
cnty <- read_csv("330_county_panel_08-16_subset.csv")

```



## Plotly Scatterplot

We'll plot basic OLS, quadratic, linear-log, and LOESS fits of the pooled data, along with the scatterplot. For the quadratic and linear-log fits, we first need to generate new columns because I haven't figured out how to get plotly to compute them _in situ_.
```{r}
cnty$hdi2 <- cnty$hdi^2
cnty$loghdi <- log(cnty$hdi)
```


Let's also get a palette for for the scatterplot markers, so we can view & filter by year.
```{r}
plotly.colors <- brewer.pal(4, "Set2")
```

Now we plot!
```{r plotly01}
cnty %>% 
  mutate(year = as_factor(year)) %>% 
  plot_ly(data = ., x = ~hdi) %>% 
  add_markers(
    y = ~to.vep,
    symbol = ~year,
    symbols = c("circle", "x", "diamond"),
    color = I("grey50"),
    opacity = 0.5,
    text = ~paste0(county, ", ", state, 
                  "<br>HDI: ", round(hdi, 2), 
                  "<br>Turnout: ", round(to.vep * 100, 1), "%"),
    hoverinfo = 'text'
  ) %>% 
  add_lines(
    y = ~fitted(lm(to.vep ~ hdi)),
    name = "OLS",
    line = list(color = plotly.colors[1], width = 4)
  ) %>% 
  add_lines(
    y = ~fitted(lm(to.vep ~ hdi + hdi2)),
    name = "Quadratic",
    line = list(color = plotly.colors[2], width = 4)
  ) %>% 
  add_lines(
    y = ~fitted(lm(to.vep ~ loghdi)),
    name = "Linear-Log",
    line = list(color = plotly.colors[3], width = 4)
  ) %>% 
  add_lines(
    y = ~fitted(loess(to.vep ~ hdi)),
    name = "LOESS",
    line = list(color = plotly.colors[4], width = 4)
  )
```

